---
title: "Assignment 1"
author: "s231861"
format: html
---

## Disclaimer

Every code for assignment 1 can be found under "Assignment_1git.R".

## Problem 1

Date: 04.10.23

Name: Daniel Bømark

Student number: s231861

## Problem 2

Solving this problem I loaded tidyverse in advance. First step is to load the
the file into our memory.

```{r}
library(tidyverse)
raw_file <- readLines(con = "suites_dw_Table1.txt")
```

Identify the line number L of the separator line between the column names and
the rest of the data table.

```{r}
#| eval: false
substr(x = raw_file,start = 1,stop = 2)
```

The next step is then to find out *which* line starts with "--", and pick out
the first one.

```{r}
L <-
  (substr(x = raw_file, start = 1, stop = 2) == "--") %>%
  which() %>%
  min()
```

Save the variable descriptions (i.e. the information in lines 1:(L-2)) in a
text-file for future reference using the cat()-function.

```{r}
cat(raw_file[1:(L-2)], sep = "\n", file = "variable_description.txt")
```

Extract the variable names (i.e. line (L-1)), store the names in a vector.

```{r}
variable_names <- 
  str_split(string = raw_file[L-1], pattern = "\\|") %>%
  unlist() %>%
  str_trim()
```

Read the data. 

```{r}
comma_separated_values <-
  raw_file[15:length(raw_file)] %>% 
  gsub("\\|", ",", .) %>% 
  gsub(" ", "", .)
```

# We then just add the variable names (separated with commas) on top

```{r}
comma_separated_values_with_names <- 
  c(paste(variable_names, collapse = ","),
    comma_separated_values)   
```

cat()-the whole ting to a .csv-file in the same way as we did with the
variable descriptions above.

```{r}
cat(comma_separated_values_with_names, sep = "\n", file = "updated_file.txt")
```

Read the file back in as a normal csv-file.

```{r}
galaxies <- read_csv("updated_file.txt")
```


## Problem 3

Loading in needed packages first (ggplot2).

Create a plot - histogram to visualize the different size of the galaxy
by using a_26 on the x-axes, we get to see the count for the different sizes
the higher the number, the smaller the galaxy.

```{r}
library(ggplot2)

galaxies %>%
  ggplot(aes(x = a_26)) +
  geom_histogram()
```

The value represents the linear diameter, and when this value increases,
the size of the galaxy gets smaller. This is caused by that it's a longer
distance to the center.

Conclussion is that the count for galaxies drops as the values increases.


## Problem 4

Didn't manage to put it in here. Can be found in the R.file..